%-------------------------
% CV - Khaled Ehab Attia
% LaTeX Template
%------------------------- 

\documentclass[a4paper,11pt]{article}

\usepackage[top=1.5cm, bottom=1.5cm, left=1.8cm, right=1.8cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

% ---- Colors ----
\definecolor{accentblue}{HTML}{2563EB}
%\definecolor{darkblue}{HTML}{00008B}

% ---- Section Formatting ----
\titleformat{\section}
  {\large\bfseries\color{accentblue}}
  {}{0em}{}
  [\color{accentblue}\titlerule]

\titlespacing*{\section}{0pt}{10pt}{6pt}

% ---- No page numbers ----
\pagestyle{empty}

% ---- Custom Commands ----
\newcommand{\cventry}[4]{%
  \textbf{#1} \hfill \textit{#3} \\
  \textit{#2} \hfill \textit{#4}
  \vspace{2pt}
}

\newcommand{\cveducation}[3]{%
  \textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\newcommand{\cvcert}[4]{%
  \textbf{#1} | \textit{#2}\hfill \textit{#4} \\
  \textit{#3}
  \vspace{2pt}
}

\newcommand{\cvproject}[2]{%
  \textbf{#1} \hfill \textit{#2}
  \vspace{2pt}
}

\begin{document}

%-------------------------
% HEADER
%-------------------------
\begin{center}
  {\LARGE\bfseries Khaled Ehab Attia} \\[3pt]
  {\Large AI Engineer} \\[5pt]
  \small
  +20 106 924 2612 $|$
  \href{mailto:kha.2002.ke@gmail.com}{kha.2002.ke@gmail.com} $|$
  \href{http://www.linkedin.com/in/khaled-ehab}{linkedin.com/in/khaled-ehab} % $|$
  \newline \href{https://github.com/Khaled100233}{github.com/Khaled100233} $|$
  Cairo, EG.
   

\end{center}

\vspace{4pt}

%-------------------------
% OBJECTIVE
%-------------------------
\section{Objective}

AI Engineer specializing in Computer Vision and LLM-powered systems, with hands-on experience building production-grade AI agents, deep learning pipelines, and teaching at university level. Skilled in Python for AI/ML — combining strong research foundations with practical engineering.

%-------------------------
% EXPERIENCE
%-------------------------
\section{Experience}



\cventry{Full Time Teaching Assistant}{German International University (GIU)}{February 2025 -- Present}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Delivered lectures, tutorials, and lab sessions as part of the official teaching load.
  \item Contributed to curriculum preparation, course content development, and instructional design.
  \item Evaluated and processed student assignments, quizzes, and exams with timely feedback.
  \item Developed and uploaded course materials, handouts, and teaching aids to the GIU Intranet.
  \item Fulfilled administrative and academic responsibilities including office hours, student advising, exam invigilation, committee assignments, and other tasks assigned by university management.
  \item Led student advising sessions and mentored junior students through complex lab implementations, demonstrating strong communication and leadership under academic pressure.
\end{itemize}
\vspace{6pt}

\cventry{Freelance AI \& Software Projects}{Self-Employed}{Dec 2025 -- Present}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Developed an AI/ML solution and conducted an individual AI project review, applying supervised learning techniques and model evaluation workflows.
  \item Designed and delivered a Data Science for Cyber Security analysis, covering threat modeling and data-driven security insights.
  \item Engineered a Robot Referee system integrating AI decision-making logic for automated real-time judgment.
  \item Investigated energy consumption patterns using data analysis and visualization techniques to derive actionable insights.
\end{itemize}
\vspace{6pt}

\cventry{Part Time Teaching Assistant}{Arab Academy for Science \& Technology (AAST)}{February 2026 -- Present}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Assisted in delivering tutorials and practical lab sessions to support students' understanding of course concepts.
  \item Supported course lecturers in preparing teaching materials, presentations, and lab exercises.
  \item Graded assignments, quizzes, and lab reports, providing constructive and timely feedback to students.
  \item Guided students during lab work, helping them troubleshoot technical and implementation issues.
  \item Contributed to course coordination tasks including attendance tracking, exam preparation, and invigilation.
\end{itemize}

\vspace{6pt}

% \cventry{Program-Based AI Instructor}{Arab Administrative Development Organization}{October 2024}{}
% \begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
%   \item Taught 30\% of the program (AI for Crisis Management).
%   \item Prepared educational content for the training program including practical applications.
%   \item Presented and clarified content to trainees and discussed up-to-date ideas in the context of the program.
% \end{itemize}

% \vspace{6pt}

\newpage

%-------------------------
% EDUCATION
%-------------------------
\section{Education}

\cveducation{German International University}{Master of Science in Data Science}{2025 -- Present}

\vspace{6pt}

% \cveducation{Sprints}{Certificaete of AI/ML}{Feb 2026 -- May 2026}

\cveducation{Arab Academy for Science and Technology}{Bachelor of Computer Science | Minor: Artificial Intelligence | GPA: 3.65 -- Excellent with Honors}{2020 -- 2024}

\vspace{6pt}

\cveducation{Information Technology Institution (ITI)}{ \textbf{Cyber Security Training -- 120H}: CCNA, Introduction to Cyber Security, Ethical Hacking, Palo Alto, FortiGate}{August 2023}

%-------------------------
% CERTIFICATES
%-------------------------
\section{Certificates \& Scholarships}
\cvcert{American Center Cairo (ACC)}{AI/ML Program -- Sprints Platform}{
  Full-stack AI/ML bootcamp covering Python, Data Analysis, Supervised \& Unsupervised Learning, 
  Deep Learning, NLP, and Generative AI. \newline
  Advanced topics include LLMs, Prompt Engineering, Agentic AI, LangChain, and RAG Pipelines 
  across \textbf{6 sprints, 38 modules, and 92 hours of structured learning}.
}{Jan 2026 -- Present}

\vspace{4pt}

% \cvcert{American Center Cairo (ACC)}{AI/ML Learning Journey Scholarship}{
%   Python, Data Analysis, Machine Learning, Deep Learning, NLP, and Generative AI. \newline
%   Topics span SWE foundations, data fluency, deep learning architectures, NLP-based generative models, and Agentic AI frameworks across \textbf{6 structured sprints (92 hours)}.
% }{Jan 2026 -- Present}

% \vspace{4pt}

\cvcert{NVIDIA Deep Learning Institute}{Fundamentals of Deep Learning}{
  Neural network architectures, model training, and optimization using GPU-accelerated computing. \newline
  Hands-on experience with deep learning frameworks and practical DL workflows.
}{Apr 2026}

\vspace{4pt}

\cvcert{365 Data Science}{Intermediate Python Programming}{Strings, Text Data, Nested Loops, List Comprehensions, Advanced Functions}{November 2024}

\vspace{4pt}

\cvcert{EF SET}{English Certificate}{67\% C1 Advanced (Reading \& Listening)}{November 2024}

%-------------------------
% PROJECTS
%-------------------------
\section{Projects}

\cvproject{\href{https://github.com/Khaled100233/Robot-Referee}{Robot Referee | Computer Vision Project}}{2026}
\newline \textit{Python, OpenCV, NumPy, Computer Vision, Object Detection, Real-Time Processing}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Developed an automated referee system using computer vision to detect game events and support real-time decision making.
  \item Built image/video processing pipelines to track players, ball movement, and field interactions.
  \item Applied object detection and rule-based logic to identify fouls, goals, and boundary violations.
  \item Designed a modular Python solution for real-time inference and scalable feature expansion.
  \item Evaluated system accuracy and generated visual outputs for performance validation.
\end{itemize}

\vspace{6pt}

\cvproject{\href{https://github.com/Seif-3mk-hassan/Sprints-capstone-project}{Reviews Sentiment API -- Full Stack AI Project}}{2026}
\newline \textit{Python, FastAPI, TextBlob, Pandas, SQLite, Docker} 
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Owned and implemented the full ETL pipeline (\texttt{etl\_pipeline.py}), handling data extraction from raw CSV, quality assessment (nulls, duplicates, type mismatches), and comprehensive data cleaning.
  \item Engineered the transformation logic including TextBlob NLP sentiment scoring and rolling average sentiment calculation per product, sorted by date.
  \item Implemented the SQLite LOAD step to persist cleaned and transformed data, with robust try/except error handling for all file I/O operations.
  \item Coordinated with teammates on database schema compatibility to ensure seamless integration with the FastAPI serving layer.
\end{itemize}

\cvproject{\href{https://github.com/Khaled100233/medicare-fraud-detection}{Medicare Fraud Detection | Machine Learning Project}}{2026}
\newline \textit{Python, Scikit-learn, Pandas, NumPy, Matplotlib, Seaborn}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Built a machine learning pipeline to detect fraudulent Medicare claims using structured healthcare data.
  \item Performed data cleaning, preprocessing, EDA, and feature engineering to improve model performance.
  \item Trained and evaluated classification models using Precision, Recall, F1-score, ROC-AUC, and cross-validation.
  \item Applied resampling techniques to address class imbalance and improve fraud detection sensitivity.
  \item Created visualizations to identify suspicious billing patterns and communicate insights.
\end{itemize}

\vspace{6pt}

\cvproject{\href{https://github.com/Khaled100233/retail-analytics-copilot}{Retail Analytics Copilot}}{2025}
\newline \textit{Python, LangGraph, DSPy, SQLite}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Built an AI agent that answers retail analytics questions by intelligently combining document retrieval (RAG) and SQL database queries.
  \item Designed an 8-node LangGraph workflow with conditional routing, automated SQL error repair, and format validation achieving 80\%+ accuracy.
  \item Optimized natural language to SQL conversion using DSPy, improving query execution success rate by 50\% through few-shot learning.
  \item Implemented TF-IDF retrieval over policy documents with citation tracking, ensuring auditable and explainable answers.
  \item Deployed a 100\% local solution using the Phi-3.5 model, processing 6 complex queries end-to-end with typed outputs and confidence scores.
\end{itemize}

\vspace{6pt}

\cvproject{Therma Ear -- Graduation Project}{2024}
\newline \textit{Python, Vision Transformer}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Implemented multiple deep learning architectures (VGG16, ResNet50, MobileNetV2, Vision Transformer) to diagnose patients via thermal ear images.
  \item Achieved 92\% accuracy in predicting Auricular Acupuncture points using the Vision Transformer model.
  \item Applied data augmentation techniques (Cropping, Rotation) to increase training data volume.
  \item Integrated an embedded thermal camera for real-time input and reviewed extensive research literature to inform the solution.
\end{itemize}

\vspace{6pt}

\cvproject{Image Stitching}{2024}
\newline \textit{Python, OpenCV}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Developed an image stitching algorithm to seamlessly merge multiple images into a panoramic image.
  \item Used feature detection and matching (ORB -- Oriented FAST and Rotated BRIEF) and perspective matching via RANSAC.
\end{itemize}

\vspace{6pt}

\cvproject{Cancer Tumor Detection by Image Processing}{2023}
\newline \textit{Python, OpenCV}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Performed image processing using Pillow and OpenCV.
  \item Implemented a modified VGG16-based deep learning model achieving 80\% accuracy and high precision in tumor classification.
  \item Evaluated models using accuracy, precision, recall, AUC, and loss metrics. Awarded best project certificate of appreciation.
\end{itemize}

\vspace{6pt}

\cvproject{Kidney Disease Detection}{2022}
\newline \textit{Python, Scikit-learn}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=-5pt]
  \item Built a machine learning model to predict kidney disease from patient text data.
  \item Tested multiple ML techniques (Linear Regression, Polynomial Regression, KNN, SVM, Logistic Regression).
  \item Achieved 95\% accuracy using Support Vector Machine.
\end{itemize}


%-------------------------
% SKILLS & ABILITIES
%-------------------------
% \section{Skills \& Abilities}

% \textbf{Soft Skills:} Communication, Presentation, Composure, Problem Solving, Critical Thinking, Leadership \& Mentoring, Time Management, Teamwork \& Collaboration, Emotional Intelligence, Adaptability.

%-------------------------
% TECHNICAL TOOLS
%-------------------------
\section{Technical Tools}

\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=2pt]
  \item \textbf{Programming Languages:} C/C++, Java, PHP, HTML/CSS, JavaScript, Python (AI \& Data Science)
  \item \textbf{Data Tools:} NumPy, Pandas
  \item \textbf{Deep Learning Frameworks:} PyTorch, TensorFlow/Keras, Transformers.
  \item \textbf{Computer Vision:} OpenCV, Pillow
  \item \textbf{Database Management:} SQL, PLSQL
  \item \textbf{Version Control:} Git, GitHub
  \item \textbf{Visualization:} Matplotlib, Seaborn.
  \item \textbf{Development Environments:} Jupyter Notebook, Google Colab, VS Code, Visual Studio, NetBeans
  \item \textbf{Graphics \& Design:} Adobe Photoshop, Adobe Illustrator, Adobe Premiere, Figma, Adobe XD
\end{itemize}

\end{document}
