%-------------------------
% CV - Khaled Ehab Attia
% LaTeX Template
%-------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[top=1.5cm, bottom=1.5cm, left=1.8cm, right=1.8cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

% ---- Colors ----
\definecolor{accentblue}{HTML}{2563EB}

% ---- Section Formatting ----
\titleformat{\section}
  {\large\bfseries\color{accentblue}}
  {}{0em}{}
  [\color{accentblue}\titlerule]

\titlespacing*{\section}{0pt}{10pt}{6pt}

% ---- No page numbers ----
\pagestyle{empty}

% ---- Custom Commands ----
\newcommand{\cventry}[4]{%
  \textbf{#1} \hfill \textit{#3} \\
  \textit{#2} \hfill \textit{#4}
  \vspace{2pt}
}

\newcommand{\cveducation}[3]{%
  \textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\newcommand{\cvcert}[3]{%
  \textbf{#1} \hfill \textit{#3} \\
  \textit{#2}
  \vspace{2pt}
}

\newcommand{\cvproject}[2]{%
  \textbf{#1} \hfill \textit{#2}
  \vspace{2pt}
}

\begin{document}

%-------------------------
% HEADER
%-------------------------
\begin{center}
  {\LARGE\bfseries Khaled Ehab Attia} \\[6pt]
  \small
  Cairo, EG \quad|\quad
  +20 106 924 2612 \quad|\quad
  \href{mailto:kha.2002.ke@gmail.com}{kha.2002.ke@gmail.com} \quad|\quad
  \href{http://www.linkedin.com/in/khaled-ehab}{linkedin.com/in/khaled-ehab} \quad|\quad
  \href{https://github.com/Khaled100233}{github.com/Khaled100233}
\end{center}

\vspace{4pt}

%-------------------------
% OBJECTIVE
%-------------------------
\section{Objective}

AI Engineer specializing in Computer Vision and LLM-powered systems, with hands-on experience building production-grade AI agents, deep learning pipelines, and teaching at university level. Skilled in Python for AI/ML — combining strong research foundations with practical engineering.

%-------------------------
% EXPERIENCE
%-------------------------
\section{Experience}

\cventry{Part Time Teaching Assistant}{Arab Academy for Science \& Technology}{February 2026 -- Present}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Assisted in delivering tutorials and practical lab sessions to support students' understanding of course concepts.
  \item Supported course lecturers in preparing teaching materials, presentations, and lab exercises.
  \item Graded assignments, quizzes, and lab reports, providing constructive and timely feedback to students.
  \item Guided students during lab work, helping them troubleshoot technical and implementation issues.
  \item Contributed to course coordination tasks including attendance tracking, exam preparation, and invigilation.
\end{itemize}

\vspace{6pt}

\cventry{Full Time Teaching Assistant}{German International University (GIU)}{February 2025 -- Present}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Delivered lectures, tutorials, and lab sessions as part of the official teaching load.
  \item Contributed to curriculum preparation, course content development, and instructional design.
  \item Evaluated and processed student assignments, quizzes, and exams with timely feedback.
  \item Developed and uploaded course materials, handouts, and teaching aids to the GIU Intranet.
  \item Fulfilled administrative and academic responsibilities including office hours, student advising, exam invigilation, committee assignments, and other tasks assigned by university management.
\end{itemize}

\vspace{6pt}

\cventry{Program-Based AI Instructor}{Arab Administrative Development Organization}{October 2024}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Taught 30\% of the program (AI for Crisis Management).
  \item Prepared educational content for the training program including practical applications.
  \item Presented and clarified content to trainees and discussed up-to-date ideas in the context of the program.
\end{itemize}

\vspace{6pt}

\cventry{Volunteer Research Assistant}{Badya University}{September 2024}{}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Conducted literature reviews and gathered relevant research materials for academic publications.
  \item Assisted in the design, development, and optimization of AI models, including data preprocessing, feature engineering, and algorithm selection.
  \item Implemented and fine-tuned machine learning and deep learning algorithms using Python.
  \item Evaluated model performance using metrics such as accuracy, precision, recall, and F1-score.
\end{itemize}

%-------------------------
% EDUCATION
%-------------------------
\section{Education}

\cveducation{German International University}{Master of Science in Data Science}{2025 -- Present}

\vspace{6pt}

\cveducation{Arab Academy for Science and Technology}{Bachelor of Computer Science \quad|\quad Minor: Artificial Intelligence \quad|\quad GPA: 3.65 -- Excellent with Honors}{2020 -- 2024}

\vspace{6pt}

\cveducation{Information Technology Institution (ITI)}{Cyber Security Training -- 120H: CCNA, Introduction to Cyber Security, Ethical Hacking, Palo Alto, FortiGate}{August 2023}

%-------------------------
% CERTIFICATES
%-------------------------
\section{Certificates}

\cvcert{365 Data Science}{Certificate of Completion -- Intermediate Python Programming (Strings, Text Data, Nested Loops, List Comprehensions, Advanced Functions)}{November 2024}

\vspace{4pt}

\cvcert{365 Data Science}{Certificate of Completion -- Introduction to Python (Variables, Syntax, Operators, Conditionals, Functions, Sequences, OOP)}{November 2024}

\vspace{4pt}

\cvcert{365 Data Science}{Certificate of Completion -- Introduction to Jupyter (Anaconda, Jupyter, Shortcuts, Error Handling, Kernels)}{November 2024}

\vspace{4pt}

\cvcert{EF SET}{English Certificate -- 67\% C1 Advanced (Reading \& Listening)}{November 2024}

\vspace{4pt}

\cvcert{MaharaTech}{Python Programming Basics (Syntax, Control Flow, Functions, Collections)}{November 2024}

\vspace{4pt}

\cvcert{MaharaTech}{Database Fundamentals (ERD, Mapping, SQL, DDL, DML, PLSQL, Normalization)}{August 2024}

%-------------------------
% PROJECTS
%-------------------------
\section{Projects}

\cvproject{Retail Analytics Copilot}{2025}
\textit{Python, LangGraph, DSPy, SQLite}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Built an AI agent that answers retail analytics questions by intelligently combining document retrieval (RAG) and SQL database queries.
  \item Designed an 8-node LangGraph workflow with conditional routing, automated SQL error repair, and format validation achieving 80\%+ accuracy.
  \item Optimized natural language to SQL conversion using DSPy, improving query execution success rate by 50\% through few-shot learning.
  \item Implemented TF-IDF retrieval over policy documents with citation tracking, ensuring auditable and explainable answers.
  \item Deployed a 100\% local solution using the Phi-3.5 model, processing 6 complex queries end-to-end with typed outputs and confidence scores.
\end{itemize}

\vspace{6pt}

\cvproject{Therma Ear -- Graduation Project}{2024}
\textit{Python, Vision Transformer}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Implemented multiple deep learning architectures (VGG16, ResNet50, MobileNetV2, Vision Transformer) to diagnose patients via thermal ear images.
  \item Achieved 92\% accuracy in predicting Auricular Acupuncture points using the Vision Transformer model.
  \item Applied data augmentation techniques (Cropping, Rotation) to increase training data volume.
  \item Integrated an embedded thermal camera for real-time input and reviewed extensive research literature to inform the solution.
\end{itemize}

\vspace{6pt}

\cvproject{Image Stitching}{2024}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Developed an image stitching algorithm to seamlessly merge multiple images into a panoramic image.
  \item Used feature detection and matching (ORB -- Oriented FAST and Rotated BRIEF) and perspective matching via RANSAC.
\end{itemize}

\vspace{6pt}

\cvproject{Cancer Tumor Detection by Image Processing}{2023}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Performed image processing using Pillow and OpenCV.
  \item Implemented a modified VGG16-based deep learning model achieving 80\% accuracy and high precision in tumor classification.
  \item Evaluated models using accuracy, precision, recall, AUC, and loss metrics. Awarded best project certificate of appreciation.
\end{itemize}

\vspace{6pt}

\cvproject{Kidney Disease Detection}{2022}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Built a machine learning model to predict kidney disease from patient text data.
  \item Tested multiple ML techniques (Linear Regression, Polynomial Regression, KNN, SVM, Logistic Regression).
  \item Achieved 95\% accuracy using Support Vector Machine.
\end{itemize}

\vspace{6pt}

\cvproject{Car Service Website}{2022}
\textit{PHP, HTML, CSS, JavaScript, Bootstrap}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Designed and developed a full-stack web application for a car services company with dynamic features and database management.
\end{itemize}

\vspace{6pt}

\cvproject{Online Ice Cream Shop}{2021}
\textit{Java, JSP, HTML, CSS}
\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=1pt]
  \item Designed and developed a full-stack web application with dynamic features and database management.
\end{itemize}

%-------------------------
% SKILLS & ABILITIES
%-------------------------
\section{Skills \& Abilities}

\textbf{Soft Skills:} Communication, Presentation, Composure, Problem Solving, Critical Thinking, Leadership \& Mentoring, Time Management, Teamwork \& Collaboration, Emotional Intelligence, Adaptability.

%-------------------------
% TECHNICAL TOOLS
%-------------------------
\section{Technical Tools}

\begin{itemize}[leftmargin=1.5em, topsep=2pt, itemsep=2pt]
  \item \textbf{Programming Languages:} C/C++, Java, PHP, HTML/CSS, JavaScript, Python (AI \& Data Science)
  \item \textbf{Data Tools:} NumPy, Pandas
  \item \textbf{Computer Vision:} OpenCV, Pillow
  \item \textbf{Database Management:} SQL, PLSQL
  \item \textbf{Version Control:} Git, GitHub
  \item \textbf{Visualization:} Matplotlib
  \item \textbf{Development Environments:} Jupyter Notebook, Google Colab, VS Code, Visual Studio, NetBeans
  \item \textbf{Graphics \& Design:} Adobe Photoshop, Adobe Illustrator, Adobe Premiere, Figma, Adobe XD
\end{itemize}

\end{document}
